---
title: BFI screen sector statistics to June 2025
author: Brian Tarran
date: last-modified
date-format: long
format: 
  revealjs:
    smaller: true
css: style.css
title-slide-attributes:
  data-background-color: "#e50076"
execute: 
  echo: false
  warning: false
embed-resources: false
---

```{r}
#| label: load-functions
#| file: R/stats.R
```

```{r}
#| label: set-file-path

file_path <- here::here('data/bfi_stats_release_data.xlsx')
```

# UK box office and admissions {background-color="#e50076"}


##

<div id="left">

In the UK in the period January to June (H1) 2025:

* Box office revenue was £496.3 million, up 18% on H1 2024 and down 17% on H1 2019.
* The highest earning film was *A Minecraft Movie*, released in the first week of April.

</div>

<div id="right">

```{r}
#| label: uk-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_box_office'
df <- load_data(file_path, sheet_name)
uk_box_office()
```

</div>

## 

<div id="left">

* There were 61 million cinema admissions, 12% higher than in H1 2024 and 27% lower
than in H1 2019.

</div>

<div id="right">

```{r}
#| label: uk-admissions
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_admissions'
df <- load_data(file_path, sheet_name)
uk_admissions()
```
</div>

## 

<div id="left">

* April recorded 2025's highest monthly admissions to date, at 11.8 million.

</div>

<div id="right">

```{r}
#| label: uk-admissions-month
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_admissions_month()
```

</div>

# UK and Republic of Ireland box office {background-color="#783df6"}

##

<div id="left">

At the UK and Republic of Ireland (ROI) box office in H1 2025:

* Revenue for films released in H1 2025 was £467.8 million, up 14% on H1 2024 and
down 20% on H1 2019.

</div>

<div id="right">

```{r}
#| label: uk-roi-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_roi_box_office'
df <- load_data(file_path, sheet_name)
uk_roi_box_office()
```

</div>

```{r}
#| label: uk-market-share
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

sheet_name <- 'uk_film_share'
df <- load_data(file_path, sheet_name)
uk_market_share()
```

```{r}
#| label: uk-market-share-indie
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

uk_market_share_indie()
```

##

<div id="left">

* The total market share of all UK qualifying films was 44.7%, almost 20 percentage points higher than H1 2024’s total UK qualifying share (26.3%).

</div>

<div id="right">

```{r}
#| label: uk-market-share-percent
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_film_share'
df <- load_data(file_path, sheet_name)
uk_market_share_percent()
```

</div>

# Film and HETV production spend {background-color="#1197FF"}

**Note:** Production spend and count are revised over time to account for lags in obtaining complete data across all types of productions. Figures for more recent periods are therefore likely to be revised upward as more information becomes available.

```{r}
#| label: set-variables-spend

sheet_name <- 'uk_production_detail'
df <- load_data(file_path, sheet_name)
metric <- 'UK_spend_m'
```

##

<div id="left">

In the UK in the rolling year July 2024 to June 2025: 

* The combined total spend on film and high-end television (HETV) production was £5.7 billion.

</div>

<div id="right">

```{r}
#| label: all-production-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

title <- 'UK production spend, £ million'
all_production_first()
```

</div>

##

<div id="left">

* Production spend for the year to June 2025 was up 18% on revised 2024 figures. 

</div>

<div id="right">

```{r}
#| label: all-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

title <- 'UK production spend, £ million' 
all_production_revised()
```

</div>

##
```{r}
#| label: film-hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production spend, £ million'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            and <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
film_hetv_production_revised()
```

##
```{r}
#| label: film-hetv-production-revised-percentage
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production spend, proportion (%) by category' 
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            and <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
film_hetv_production_revised_percentage()
```

##
```{r}
#| label: film-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production spend, £ million'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in year to March"
production_revised()
```

##
```{r}
#| label: film-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production spend, £ million'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in year to March"
production_breakdown_revised()
```

##
```{r}
#| label: hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production spend, £ million'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
production_revised()
```

##
```{r}
#| label: hetv-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production spend, £ million'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
production_breakdown_revised()
```

# Film and HETV production count {background-color="#1197FF"}

**Note:** Production spend and count are revised over time to account for lags in obtaining complete data across all types of productions. Figures for more recent periods are therefore likely to be revised upward as more information becomes available.

```{r}
#| label: set-variables-count
#| eval: false

sheet_name <- 'uk_production_detail'
df <- load_data(file_path, sheet_name)
metric <- 'count'
```

##
```{r}
#| label: all-production-count-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production count'
subtitle <- "For film and HETV starting principal photography in calendar year, 
            <span style='color:#783df6'>**first reported**</span>"
all_production_first()
```

##
```{r}
#| label: all-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production count'
subtitle <- "For film and HETV starting principal photography in calendar year, 
            <span style='color:#783df6'>**first reported**</span> and 
            <span style='color:darkgrey'>**revised**</span>"
all_production_revised()
```

##
```{r}
#| label: film-hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production count' 
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            and <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March" 
film_hetv_production_revised()
```

##
```{r}
#| label: film-hetv-production-count-revised-percentage
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production count, proportion (%) by category' 
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            and <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
film_hetv_production_revised_percentage()
```

##
```{r}
#| label: film-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production count'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in year to March"
production_revised()
```

##
```{r}
#| label: film-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production count'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in year to March"
production_breakdown_revised()
```

##
```{r}
#| label: hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production count'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
production_revised()
```

##
```{r}
#| label: hetv-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production count'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
production_breakdown_revised()
```

# Sources {background-color="#e50076"}

* Box office: Comscore
* Admissions: Cinema Advertising Association
* Production: BFI Research & Statistics Unit 

See [bfi.org.uk](https://www.bfi.org.uk/industry-data-insights) for more industry data and insights