---
title: BFI Q1 2025 screen sector statistics
author: Ian Cade
date: last-modified
date-format: long
format: revealjs
title-slide-attributes:
  data-background-color: "#e50076"
execute: 
  echo: false
  warning: false
embed-resources: false
---

```{r}
#| label: load-functions
#| file: R/stats.R
```

```{r}
#| label: set-file-path

file_path <- here::here('data/bfi_stats_release_data.xlsx')
```

# UK box office and admissions {background-color="#e50076"}

##
```{r}
#| label: uk-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

sheet_name <- 'uk_box_office'
df <- load_data(file_path, sheet_name)
uk_box_office()
```

##
```{r}
#| label: uk-admissions
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_admissions'
df <- load_data(file_path, sheet_name)
uk_admissions()
```

## 
```{r}
#| label: uk-admissions-month
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_admissions_month()
```

# UK and Republic of Ireland box office {background-color="#783df6"}

##
```{r}
#| label: uk-roi-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

sheet_name <- 'uk_roi_box_office'
df <- load_data(file_path, sheet_name)
uk_roi_box_office()
```

##
```{r}
#| label: uk-market-share
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

sheet_name <- 'uk_film_share'
df <- load_data(file_path, sheet_name)
uk_market_share()
```

##
```{r}
#| label: uk-market-share-indie
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

uk_market_share_indie()
```

##
```{r}
#| label: uk-market-share-percent
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

sheet_name <- 'uk_film_share'
df <- load_data(file_path, sheet_name)
uk_market_share_percent()
```

# Film and HETV production spend {background-color="#1197FF"}

**Note:** Production spend and count are revised over time to account for lags in obtaining complete data across all types of productions. Figures for year ending March 2025 are therefore likely to be revised upward as more
information becomes available in subsequent periods.

```{r}
#| label: set-variables-spend
#| eval: false

sheet_name <- 'uk_production_detail'
df <- load_data(file_path, sheet_name)
metric <- 'UK_spend_m'
```

##
```{r}
#| label: all-production-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production spend, £ million'
subtitle <- "For film and HETV starting principal photography in calendar year, 
            <span style='color:#783df6'>**first reported**</span>"
all_production_first()
```

##
```{r}
#| label: all-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production spend, £ million' 
subtitle <- "For film and HETV starting principal photography in calendar year, 
            <span style='color:#783df6'>**first reported**</span> and 
            <span style='color:darkgrey'>**revised**</span>"
all_production_revised()
```

##
```{r}
#| label: film-hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production spend, £ million'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            and <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
film_hetv_production_revised()
```

##
```{r}
#| label: film-hetv-production-revised-percentage
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production spend, proportion (%) by category' 
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            and <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
film_hetv_production_revised_percentage()
```

##
```{r}
#| label: film-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production spend, £ million'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in year to March"
production_revised()
```

##
```{r}
#| label: film-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production spend, £ million'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in year to March"
production_breakdown_revised()
```

##
```{r}
#| label: hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production spend, £ million'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
production_revised()
```

##
```{r}
#| label: hetv-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production spend, £ million'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
production_breakdown_revised()
```

# Film and HETV production count {background-color="#1197FF"}

**Note:** Production spend and count are revised over time to account for lags in obtaining complete data across all types of productions. Figures for year ending March 2025 are therefore likely to be revised upward as more
information becomes available in subsequent periods.

```{r}
#| label: set-variables-count
#| eval: false

sheet_name <- 'uk_production_detail'
df <- load_data(file_path, sheet_name)
metric <- 'count'
```

##
```{r}
#| label: all-production-count-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production count'
subtitle <- "For film and HETV starting principal photography in calendar year, 
            <span style='color:#783df6'>**first reported**</span>"
all_production_first()
```

##
```{r}
#| label: all-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production count'
subtitle <- "For film and HETV starting principal photography in calendar year, 
            <span style='color:#783df6'>**first reported**</span> and 
            <span style='color:darkgrey'>**revised**</span>"
all_production_revised()
```

##
```{r}
#| label: film-hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production count' 
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            and <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March" 
film_hetv_production_revised()
```

##
```{r}
#| label: film-hetv-production-count-revised-percentage
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

title <- 'UK production count, proportion (%) by category' 
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            and <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
film_hetv_production_revised_percentage()
```

##
```{r}
#| label: film-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production count'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in year to March"
production_revised()
```

##
```{r}
#| label: film-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production count'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in year to March"
production_breakdown_revised()
```

##
```{r}
#| label: hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production count'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
production_revised()
```

##
```{r}
#| label: hetv-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production count'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in year to March"
production_breakdown_revised()
```

# Sources {background-color="#e50076"}

* Box office: Comscore
* Admissions: Cinema Advertising Association
* Production: BFI Research & Statistics Unit 

See [bfi.org.uk](https://www.bfi.org.uk/industry-data-insights) for more industry data and insights