---
title: 2024 screen sector statistics
author: Brian Tarran
date: last-modified
date-format: long
format: revealjs
title-slide-attributes:
  data-background-color: "#e50076"
execute: 
  eval: true
  echo: false
  warning: false
embed-resources: false
---

```{r}
#| label: load-functions
#| file: R/stats.R
```

```{r}
#| label: set-file-path

file_path <- here::here('data/stats.xlsx')
```

# UK box office and admissions {background-color="#e50076"}

##
```{r}
#| label: uk-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_box_office'
df <- load_data(file_path, sheet_name)
uk_box_office()
```

##
```{r}
#| label: uk-admissions
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_admissions'
df <- load_data(file_path, sheet_name)
uk_admissions()
```

## 
```{r}
#| label: uk-admissions-month
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_admissions_month()
```

# UK and Republic of Ireland box office {background-color="#783df6"}

##
```{r}
#| label: uk-roi-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_roi_box_office'
df <- load_data(file_path, sheet_name)
uk_roi_box_office()
```

##
```{r}
#| label: uk-market-share
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

sheet_name <- 'uk_film_share'
df <- load_data(file_path, sheet_name)
uk_market_share()
```

##
```{r}
#| label: uk-market-share-indie
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_market_share_indie()
```

##
```{r}
#| label: uk-market-share-percent
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

uk_market_share_percent()
```

# Film and HETV production spend {background-color="#1197FF"}

**Note:** Production spend and count are revised over time to account for lags in obtaining complete data across all types of productions. Figures for 2024 are therefore likely to be revised upward as more
information becomes available in subsequent periods.

```{r}
#| label: set-variables-spend

sheet_name <- 'uk_production_detail'
df <- load_data(file_path, sheet_name)
metric <- 'UK_spend_m'
```

##
```{r}
#| label: all-production-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
title <- 'UK production spend, £ million'
subtitle <- "For film and HETV starting principal photography in calendar year, 
            <span style='color:#783df6'>**first reported**</span>"
all_production_first()
```

##
```{r}
#| label: all-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

title <- 'UK production spend, £ million' 
subtitle <- "For film and HETV starting principal photography in calendar year, 
            <span style='color:#783df6'>**first reported**</span> and 
            <span style='color:darkgrey'>**revised**</span>"
all_production_revised()
```

##
```{r}
#| label: film-hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

title <- 'UK production spend, £ million'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            and <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in calendar year"
film_hetv_production_revised()
```

##
```{r}
#| label: film-hetv-production-revised-percentage
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

film_hetv_production_revised_percentage()
```

##
```{r}
#| label: film-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production spend, £ million'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in calendar year"
production_revised()
```

##
```{r}
#| label: film-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production spend, £ million'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in calendar year"
production_breakdown_revised()
```

##
```{r}
#| label: hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production spend, £ million'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in calendar year"
production_revised()
```

##
```{r}
#| label: hetv-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production spend, £ million'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in calendar year"
production_breakdown_revised()
```

# Film and HETV production count {background-color="#1197FF"}

**Note:** Production spend and count are revised over time to account for lags in obtaining complete data across all types of productions. Figures for 2024 are therefore likely to be revised upward as more
information becomes available in subsequent periods.

```{r}
#| label: set-variables-count

sheet_name <- 'uk_production_detail'
df <- load_data(file_path, sheet_name)
metric <- 'count'
```

##
```{r}
#| label: all-production-count-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
title <- 'UK production count'
subtitle <- "For film and HETV starting principal photography in calendar year, 
            <span style='color:#783df6'>**first reported**</span>"
all_production_first()
```

##
```{r}
#| label: all-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

title <- 'UK production count'
subtitle <- "For film and HETV starting principal photography in calendar year, 
            <span style='color:#783df6'>**first reported**</span> and 
            <span style='color:darkgrey'>**revised**</span>"
all_production_revised()
```

##
```{r}
#| label: film-hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

title <- 'UK production count' 
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            and <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in calendar year" 
film_hetv_production_revised()
```

##
```{r}
#| label: film-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production count'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in calendar year"
production_revised()
```

##
```{r}
#| label: film-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
category_colour <- '#e50076'
title <- 'Film production count'
subtitle <- "For <span style='color:#e50076'>**film**</span> 
            starting principal photography in calendar year"
production_breakdown_revised()
```

##
```{r}
#| label: hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production count'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in calendar year"
production_revised()
```

##
```{r}
#| label: hetv-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
category_colour <- '#1197FF'
title <- 'HETV production count'
subtitle <- "For <span style='color:#1197FF'>**HETV**</span> 
            starting principal photography in calendar year"
production_breakdown_revised()
```