---
title: BFI screen sector statistics to June 2025
author: Brian Tarran
date: last-modified
date-format: long
format: 
  revealjs:
    smaller: true
css: style.css
title-slide-attributes:
  data-background-color: "#e50076"
execute: 
  echo: false
  warning: false
  eval: false
embed-resources: false
---

```{r}
#| label: load-functions
#| file: R/stats.R
#| eval: true
```

```{r}
#| label: set-file-path
#| eval: true

file_path <- here::here('data/bfi_stats_release_data.xlsx')
```

# UK box office and admissions {background-color="#e50076"}


##

<div id="left">

In the UK in the period January to June (H1) 2025:

* Box office revenue was £496 million, up 18% on H1 2024 and down 17% on H1 2019.

</div>

<div id="right">

```{r}
#| label: uk-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: true


sheet_name <- "uk_box_office"
data_and_vars <- load_data(file_path, sheet_name)
uk_box_office()
```

</div>

## 

<div id="left">

* There were 61 million cinema admissions, 12% higher than in H1 2024 and 27% lower
than in H1 2019.
* Figures are for all films on release, including event releases and those that started their release prior to the H1 period.

</div>

<div id="right">

```{r}
#| label: uk-admissions
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: true


sheet_name <- 'uk_admissions'
data_and_vars <- load_data(file_path, sheet_name)
uk_admissions()
```
</div>

## 

<div id="left">

* April recorded 2025's highest monthly admissions to date, at 11.8 million.
* *A Minecraft Movie*, 2025's top-earning film so far, was released in the first week of April.

</div>

<div id="right">

```{r}
#| label: uk-admissions-month
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: true

uk_admissions_month()
```

</div>

# UK and Republic of Ireland box office {background-color="#783df6"}

##

<div id="left">

At the UK and Republic of Ireland (ROI) box office:

* Revenue for films released in H1 2025 was £467.8 million, up 14% on H1 2024 and
down 20% on H1 2019.
* This excludes event releases.

</div>

<div id="right">

```{r}
#| label: uk-roi-box-office
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: true

sheet_name <- 'uk_roi_box_office'
data_and_vars <- load_data(file_path, sheet_name)
uk_roi_box_office()
```

</div>

```{r}
#| label: uk-market-share
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

sheet_name <- 'uk_film_share'
df <- load_data(file_path, sheet_name)
uk_market_share()
```

```{r}
#| label: uk-market-share-indie
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

uk_market_share_indie()
```

##

<div id="left">

* The total market share of all UK qualifying films was just shy of 45%, almost 20 percentage points higher than H1 2024’s UK qualifying share.
* *Note*: 2025 figures in chart sum to 44% due to rounding.

</div>

<div id="right">

```{r}
#| label: uk-market-share-percent
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: true


sheet_name <- 'uk_film_share'
data_and_vars <- load_data(file_path, sheet_name)
uk_market_share_percent()
```

</div>

# Film and HETV production spend {background-color="#1197FF"}

```{r}
#| label: set-variables-spend

sheet_name <- 'uk_production_detail'
df <- load_data(file_path, sheet_name)
metric <- 'UK_spend_m'
```

##

<div id="left">

In the UK, in the 12 months to June 2025: 

* The combined total spend on film and high-end television (HETV) production was £5.7 billion.
* This graph shows the figures that were 'first reported' for production spend in each 12-month period. 

</div>

<div id="right">

```{r}
#| label: all-production-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_first()
```

</div>

##

<div id="left">

* Production data is revised every period to account for lags in obtaining complete data across all types of productions.
* Combined spend for the 12 months to June 2025 was up 18% on revised figures for the previous 12-month period.

</div>

<div id="right">

```{r}
#| label: all-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_revised()
```

</div>

##

<div id="left">

* HETV accounted for 64% of UK production spend in the 12 months to June 2025.

</div>

<div id="right">

```{r}
#| label: film-hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

film_hetv_production_revised()
```

</div>

```{r}
#| label: film-hetv-production-revised-percentage
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

film_hetv_production_revised_percentage()
```

##

<div id="left">

* UK spend on film production was £2.1 billion, up 18% compared with revised figures for the 12 months ending June 2024.

</div>

<div id="right">

```{r}
#| label: film-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_revised()
```

</div>

##

<div id="left">

The BFI assigns productions to one of three categories:

* Inward investment features (INW)
* Domestic UK features (DOM)
* Co-productions (COP)

See [notes to statistics releases](https://www.bfi.org.uk/industry-data-insights/official-statistics-release-calendar) for full definitions.

</div>

<div id="right">

```{r}
#| label: film-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_breakdown_revised()
```

</div>

##

<div id="left">

* UK spend on HETV projects was £3.7 billion in the 12 months to June 2025, up 18% on revised figures for the previous 12-month period.

</div>

<div id="right">

```{r}
#| label: hetv-production-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_revised()
```

</div>

##

<div id="left">

* Growth was driven by an increase in spend on inward investment programmes (INW).

</div>

<div id="right">

```{r}
#| label: hetv-production-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_breakdown_revised()
```

</div>

# Film and HETV production count {background-color="#1197FF"}

```{r}
#| label: set-variables-count

sheet_name <- 'uk_production_detail'
df <- load_data(file_path, sheet_name)
metric <- 'count'
```

##

<div id="left">

In the UK, in the 12 months to June 2025:

* Combined production starts were up 3% on first reported figures for the 12 months to June 2024.

</div>

<div id="right">

```{r}
#| label: all-production-count-first
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_first()
```

</div>

##

<div id="left">

* Production count for the 12 months to June 2025 is lower than for the other periods shown here. However, as previously noted, figures are likely to be revised upward in subsequent statistical releases as more data becomes available.

</div>

<div id="right">

```{r}
#| label: all-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

all_production_revised()
```

</div>

##

<div id="left">

* We saw earlier that HETV accounted for the majority of UK production spend in the 12 months to June 2025. Film, however, accounted for the majority of productions: 55%.

</div>

<div id="right">

```{r}
#| label: film-hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

film_hetv_production_revised()
```

</div>

```{r}
#| label: film-hetv-production-count-revised-percentage
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150
#| eval: false

film_hetv_production_revised_percentage()
```

##

<div id="left">

* 196 films were recorded as starting principal photography in the UK in the 12 months to June 2025.

</div>

<div id="right">

```{r}
#| label: film-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_revised()
```

</div>

##

<div id="left">

* Lags in obtaining complete data on production activity tend to disproportionately affect counts for domestic UK feature films (DOM), particularly those with budgets of less than £500,000. 

</div>

<div id="right">

```{r}
#| label: film-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
production_breakdown_revised()
```

</div>

##

<div id="left">

* 159 HETV programmes were recorded as starting principal photography in the UK in the 12 months to June 2025.

</div>

<div id="right">

```{r}
#| label: hetv-production-count-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_revised()
```

</div>

##

<div id="left">

* HETV programme starts in the 12 months to June 2025 included 22 feature-length single episode productions. 

</div>

<div id="right">

```{r}
#| label: hetv-production-count-breakdown-revised
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
production_breakdown_revised()
```

</div>

# Certification {background-color="#e94e24"}

```{r}
#| label: load-cert

sheet_name <- 'certification'
df <- load_data(file_path, sheet_name)
```

##

<div id="left">

In the 12 months to June 2025:

* A total of 597 films received final certification, either under the cultural test or as an official co-production.
* Certification is required to access UK tax reliefs and credits for audiovisual and video game expenditure.

</div>

<div id="right">

```{r}
#| label: film-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
cert_status_select <- 'final'
metric <- 'count'
certification()
```

</div>

##

<div id="left">

* Films achieving final certification in the 12 months to June 2025 had an associated UK production spend of £2.6 billion.
* Films and other productions can apply for final certification when they have completed production and are ready to be released.

</div>

<div id="right">

```{r}
#| label: film-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'film'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
certification()
```

</div>

##

<div id="left">

* 300 HETV titles received final certification through the cultural test in the 12 months to June 2025.
* There was one co-production with final certification but its details are not included for disclosure control reasons.

</div>

<div id="right">

```{r}
#| label: hetv-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
cert_status_select <- 'final'
metric <- 'count'
certification()
```

</div>

##

<div id="left">

* HETV productions receiving final certification under the cultural test in the 12 months to June 2025 had a UK production spend of £5.3 billion.

</div>

<div id="right">

```{r}
#| label: hetv-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'hetv'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
certification()
```

</div>

##

<div id="left">

* 94 animation television programmes received final certification under the cultural test in the 12 months to June 2025.

</div>

<div id="right">

```{r}
#| label: animation-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'animation_tv'
cert_status_select <- 'final'
metric <- 'count'
certification()
```

</div>

##

<div id="left">

* Animation TV productions receiving final certification under the cultural test in the 12 months to June 2025 had a UK production spend of £208 million.

</div>

<div id="right">

```{r}
#| label: animation-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'animation_tv'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
certification()
```

</div>

##

<div id="left">

* 119 children’s television programmes received final certification under the cultural test in the 12 months to June 2025.
* There was one co-production with final certification but its details are not included for disclosure control reasons.

</div>

<div id="right">

```{r}
#| label: childrens-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'childrens_tv'
cert_status_select <- 'final'
metric <- 'count'
certification()
```

</div>

##

<div id="left">

* Children's TV productions receiving final certification under the cultural test in the 12 months to June 2025 had a UK production spend of £221 million -- due, in part, to a small number of high-budget productions.

</div>

<div id="right">

```{r}
#| label: childrens-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'childrens_tv'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
certification()
```

</div>

##

<div id="left">

* 257 video games received final certification in the 12 months to June 2025.
* Video games can only be certified under the cultural test.

</div>

<div id="right">

```{r}
#| label: video-games-cert-final-count
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'video_games'
cert_status_select <- 'final'
metric <- 'count'
certification()
```

</div>

##

<div id="left">

* Video games receiving final certification in the 12 months to June 2025 had a UK production spend of £559 million.
* This is the second highest UK spend figure on record.

</div>

<div id="right">

```{r}
#| label: video-games-cert-final-spend
#| fig-width: 8
#| fig-height: 6
#| fig-align: center
#| fig-dpi: 150

category_select <- 'video_games'
cert_status_select <- 'final'
metric <- 'uk_spend_m'
certification()
```

</div>

# Sources {background-color="#e50076"}

* Box office: Comscore, BFI Research & Statistics Unit
* Admissions: Cinema Advertising Association
* Production: BFI Research & Statistics Unit
* Certification: BFI Research & Statistics Unit, BFI Certification Unit 

See [bfi.org.uk](https://www.bfi.org.uk/industry-data-insights) for more industry data and insights